Psychological Needs During Intergroup Contact

### 2022-01-10 Methods-and-Results.Rmd
robust meta added

robustMetaTbl <- robustMetaTbl %>%
  arrange(formula, match(
    coef,
    c(
      "CoreNeed_zwc",
      "OutgroupInteraction_zwc",
      "CoreNeed_zwc.OutgroupInteraction_zwc",
      "Autonomy_zwc",
      "Competence_zwc",
      "Relatedness_zwc",
      "CoreNeed_zwc"
    )
  )) %>% 
  mutate(formula = gsub(" \\+ \\(.*", "", formula))

robustMetaContact <-
  metaLmerOut(
    lmerDataTbl = robustMetaTbl %>% filter(formula == "AttitudesDutch ~ CoreNeed_cwc * OutgroupInteraction"),
    type = "FE",
    name = "RobustContact",
    title = "Attitudes ~ CoreNeed * Outgroup Interaction"
  )

robustMetaSDT <-
  metaLmerOut(
    lmerDataTbl = theoryMetaTblNoAllport %>% filter(formula == "QualityRaw ~ CoreNeed"),
    type = "FE",
    name = "TheoryQualityCore",
    title = "QualityRaw ~ CoreNeed"
  )

TheoryMetaAttitudeNeedQuality <-
  metaLmerOut(
    lmerDataTbl = theoryMetaTblNoAllport %>% filter(formula == "Attitude ~ CoreNeed + Quality"),
    type = "FE",
    name = "TheoryAttitudeCoreQuality",
    title = "Attitude ~ CoreNeed + Quality"
  )

>>>>

robustMetaTbl <- robustMetaTbl %>%
  arrange(formula, match(
    coef,
    c(
      "CoreNeed_zwc",
      "OutgroupInteraction_zwc",
      "CoreNeed_zwc.OutgroupInteraction_zwc",
      "Autonomy_zwc",
      "Competence_zwc",
      "Relatedness_zwc"
    )
  )) %>% 
  mutate(formula = gsub(" \\+ \\(.*", "", formula))

robustMetaContact <-
  metaLmerOut(
    lmerDataTbl = robustMetaTbl %>% filter(formula == "AttitudesDutch ~ CoreNeed_cwc * OutgroupInteraction"),
    type = "FE",
    name = "RobustContact",
    title = "Robustness — Contact and Need Fulfillment"
  )

robustMetaSDT <-
  metaLmerOut(
    lmerDataTbl = robustMetaTbl %>% filter(formula == "AttitudesDutch ~ CoreNeed_cwc + Competence_cwc + Autonomy_cwc +      Relatedness_cwc"),
    type = "FE",
    name = "RobustSDT",
    title = "Robustness — Other Needs"
  )
```
